A self-consistency check for unitary propagation of Hawking quanta

### 2016-12-08 Draft_BH_shells.tex
footnote
in discussion, regarding the the value of geometric uncertainty and
sourcing it from Hawking radiation itself.

In this paper, we proposed a self-consistency check of QFT in curved spacetime geometries.
We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
As explained in Sec.\ref{sec-BlackHole}, checking for consistency requires us to parametrize the uncertainty in the classical geometry.
We have chosen a particular form of uncertainty in our explicit calculation.
Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.

@@

>>>>

In this paper, we proposed a self-consistency check of QFT in curved spacetime geometries.
We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
As explained in Sec.\ref{sec-BlackHole}, checking for consistency requires us to parametrize the uncertainty in the classical geometry.
We have chosen a particular form of uncertainty in our explicit calculation.
Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty.

@@

Note that our argument will fail if the combination $(\sigma\Delta l)$ is exactly zero instead of a fixed finite number.
Namely, if there is absolutely no geometric uncertainty, then the geometry is indeed a completely classical system that does not entangle with the quantum field.
We would like to argue that in the context of QFT in curved spacetime, enforcing $\Delta g_{\mu\nu}=0$ is quite unreasonable.
After all, we are feeding the expectation value of the stress-tensor-operator, $\langle T_{\mu\nu}\rangle$, to the Einstein equation. 
As long as we are not in an energy eigenstate of the quantum field, $\langle\Delta T_{\mu\nu}\rangle$ will be nonzero, and there is no reason why this does not lead to an uncertainty in the geometry.
One can even use the uncertainty in the energy flux of Hawking radiation itself to argue that there has to be an uncertainty in geometry.
\footnote{Although, if one simply blue shifts the actual out-going Hawking radiation back to the hear-horizon zone, one gets a contribution of $(\sigma\Delta l)$ that depends on $M$.
That is because the QFT modes escaping the angular-momentum barrier are mostly in $S$-waves.
This $S$-wave energy flux gets diluted by area, resulting $(\sigma\Delta l)\propto M^{-2}$.
If this is the only contribution to $(\sigma\Delta l)$, such dependence exactly stops Eq.~(\ref{fin-result}) from diverging in the large black hole limit, which undermines our main argument in this paper.
Nevertheless, it violates equivalence principle for the local property $(\sigma\Delta l)$ to depend on the size of the black hole.
It will be interesting to explicitly compute $\langle\Delta T_{\mu\nu}\rangle$ for the actual states of near-horizon QFT modes to see whether they uphold equivalence principle.
Note that higher angular modes are all excited near the horizon.
They are trapped by the angular momentum barrier thus do not contribute to the asymptotic flux, but they should still contribute to local quantities.
That is why the $S$-wave contribution might be a dramatic underestimation, and the actual $(\sigma\Delta l)$ can still respect equivalence principle.
If that is true, our arguments will hold.
We will leave that particularly involved QFT calculation to future works.
 }
